## Data Preprocessing

```{r,warning=FALSE,message=FALSE}
# Importing dataset

dataset <- read.csv("Data.csv")

```

## Missing Data - Continuos data

```{r,warning=FALSE,message=FALSE}
# Missing datas
dataset

dataset$Age <- ifelse(is.na(dataset$Age),mean(dataset$Age, na.rm = TRUE),dataset$Age)

dataset$Salary <- ifelse(is.na(dataset$Salary),mean(dataset$Salary, na.rm = TRUE),dataset$Salary)

dataset

```

## One hot Encoding 

```{r,warning=FALSE,message=FALSE}
# One hot encoding for categorical data

dataset$Country <- factor(dataset$Country, 
                          levels = c("France","Spain","Germany"),
                          labels = c(1,2,3))

dataset$Purchased <- factor(dataset$Purchased, 
                          levels = c("No","Yes"),
                          labels = c(0,1))

head(dataset)
```



## Splitting Train and Test data

```{r,warning=FALSE,message=FALSE}
require(caTools)

set.seed(123)

split <- sample.split(dataset$Purchased,SplitRatio = 0.8)

train <- subset(dataset,split == TRUE)
test <- subset(dataset,split == FALSE)

```

## Feature Scaling

Machine learning models are based on Euclidian Distance. Euclidean distance is square root of sum of squares of two co-ordinates. If one of the co-ordinate has a larger scale, the distance will be dominated by that variable. Hence feature scaling is required.

```{r,warning=FALSE,message=FALSE}
train[2:3] <- scale(train[2:3])
test[2:3] <- scale(test[2:3])
head(train)
```

